---
title: "Intakes by Mandated Reporter Neighborhood-Level Report"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: kable
params: 
  d: d
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(knitr)
```

```{r, eval = T}
d <- params$d
tract_to_neighborhood <- readRDS('/app/tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

```{r, eval = F}
d <- read_csv('test/simulated_jfs_data_geocoded.csv',
              col_types = cols(INTAKE_ID = col_character(),
                               SCREENING_DECISION = col_character(),
                               DECISION_DATE = col_date(),
                               PERSON_ID = col_character(),
                               RACE = col_character(),
                               ADDRESS_START = col_date(),
                               MANDATED_REPORTER = col_character(),
                               # REPORTER_PERSON_ID = col_character(),
                               PROVIDER_ID = col_character(),
                               PROVIDER_NAME = col_character(),
                               address_type = col_character(),
                               address = col_character(),
                               bad_address = col_logical(),
                               PO = col_logical(),
                               lat = col_double(),
                               lon = col_double(),
                               score = col_double(),
                               precision = col_character(),
                               precise_geocode = col_logical(),
                               fips_tract_id = col_character(),
                               fraction_assisted_income = col_double(),
                               fraction_high_school_edu = col_double(),
                               median_income = col_double(),
                               fraction_no_health_ins = col_double(),
                               fraction_poverty = col_double(),
                               fraction_vacant_housing = col_double(),
                               dep_index = col_double()
                               ))

tract_to_neighborhood <- readRDS('tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

# Overall Summary

```{r}
date_min <- min(d$DECISION_DATE)
date_max <- max(d$DECISION_DATE)

# consider 'SCREENED IN AR' same as 'SCREENED IN'
for (i in 1:nrow(d)) {
  if (d$SCREENING_DECISION[i] == 'SCREENED IN AR') {
  d$SCREENING_DECISION[i] <- 'SCREENED IN'
}
}
```

- This report summarizes `r length(unique(d$INTAKE_ID))` intakes with descision dates between `r date_min` and `r date_max`. 

```{r}
d_missing_alleg_add <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS', 
         is.na(address)) %>% 
  select(INTAKE_ID:address_type)

d_fill_in_address <- d %>% 
  filter(INTAKE_ID %in% d_missing_alleg_add$INTAKE_ID, 
         address_type == 'CHILD_ADDRESS') %>% 
  group_by(INTAKE_ID) %>% 
  arrange(desc(ADDRESS_START)) %>% 
  slice(1) %>% 
  select(INTAKE_ID, address:dep_index)

d_missing_alleg_add <- left_join(d_missing_alleg_add, d_fill_in_address, by = 'INTAKE_ID')

d <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS' & !is.na(address) |
           address_type == 'CHILD_ADDRESS') %>% 
  bind_rows(d_missing_alleg_add) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS')
```

```{r}
### Geocoding Summary
d_intake <- filter(d, !duplicated(INTAKE_ID)) %>% 
  select(-PERSON_ID, -RACE, -ADDRESS_START,
         -address_type)

intake_geocode_summary <- d_intake %>% 
  group_by(is.na(lat)) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1))
```


```{r}
### Mandated Reporter Summary
d_mandated <- d %>% 
  filter(MANDATED_REPORTER == 'Yes')

d_mandated_intakes <- unique(d_mandated$INTAKE_ID)

d_intake <- d_intake %>% 
  mutate(at_least_one_mandated_reporter = ifelse(INTAKE_ID %in% d_mandated_intakes, 'yes', 'no'))
```

- Some intakes have more than one reporter listed. Here, an intake is considered to reported by a mandated reporter if at least one reporter listed is a mandated reporter. `r length(d_mandated_intakes)` (`r round(length(d_mandated_intakes)/length(unique(d$INTAKE_ID))*100,1)`%) intakes were reported by at least one mandated reporter.

```{r}
mr_summary <- d_intake %>% 
  filter(!is.na(lat)) %>% 
  group_by(at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>%
  ungroup() %>% 
  mutate(pct = round(n/sum(n)*100,1)) %>% 
  select(`At Least One Mandated Reporter` = at_least_one_mandated_reporter, 
         Decision = SCREENING_DECISION, n, pct)
```

The table below summarizes intakes, screening decision and mandated reporter statusby neighborhood. The table can be sorted by clicking on the column name or searched using the search box. Cells with <5 have been censored for privacy purposes.

```{r}
d_neigh_intake <- d_intake  %>%
  mutate(fips_tract_id = as.character(fips_tract_id)) %>% 
  filter(!is.na(lat)) %>% 
  left_join(tract_to_neighborhood, by='fips_tract_id')

intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood) %>% 
  summarize(n_intakes = n())

intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, SCREENING_DECISION) %>% 
  tally() %>% 
  ungroup() %>% 
  filter(SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_intakes_screened_in = n) %>% 
  select(-n, -SCREENING_DECISION) %>% 
  left_join(intakes_neighborhood, by = 'neighborhood')

##
mr_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter) %>% 
  summarize(n_mandated_reporter_intakes = n()) %>% 
  ungroup() %>% 
  filter(at_least_one_mandated_reporter == 'yes') %>% 
  select(-at_least_one_mandated_reporter)

mr_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  ungroup() %>% 
  filter(at_least_one_mandated_reporter == 'yes', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_mandated_reporter_intakes_screened_in = n) %>% 
  select(neighborhood, n_mandated_reporter_intakes_screened_in) %>% 
  left_join(mr_intakes_neighborhood, by = 'neighborhood')

##

nmr_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter) %>% 
  summarize(n_nonmandated_reporter_intakes = n()) %>% 
  ungroup() %>% 
  filter(at_least_one_mandated_reporter == 'no') %>% 
  select(-at_least_one_mandated_reporter)

nmr_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  ungroup() %>% 
  filter(at_least_one_mandated_reporter == 'no', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_nonmandated_reporter_intakes_screened_in = n) %>% 
  select(neighborhood, n_nonmandated_reporter_intakes_screened_in) %>% 
  left_join(nmr_intakes_neighborhood, by = 'neighborhood')

d_neighborhood <- intake_screen_neighborhood %>% 
  left_join(mr_intake_screen_neighborhood, by = 'neighborhood') %>% 
  left_join(nmr_intake_screen_neighborhood, by = 'neighborhood')

d_neighborhood <- neighborhood_shp %>% 
  left_join(d_neighborhood, by = 'neighborhood') %>% 
  mutate_at(vars(n_intakes, n_intakes_screened_in, 
                 n_mandated_reporter_intakes, 
                 n_mandated_reporter_intakes_screened_in,
                 n_nonmandated_reporter_intakes, 
                 n_nonmandated_reporter_intakes_screened_in), 
            ~ifelse(.x < 5, NA, .x)) %>%  # suppress if n < 5 for privacy reasons
  mutate(#n_intakes_per_1000hh = n_intakes/num_hh*1000,
         intake_fractional_screen_in = n_intakes_screened_in/n_intakes,
        # n_intakes_by_mandated_reporter_per_1000hh = n_mandated_reporter_intakes/num_hh*1000,
         intake_by_mandated_reporter_fractional_screen_in = n_mandated_reporter_intakes_screened_in/n_mandated_reporter_intakes,
       #  n_intakes_by_nonmandated_reporter_per_1000hh = n_nonmandated_reporter_intakes/num_hh*1000,
         intake_by_nonmandated_reporter_fractional_screen_in = n_nonmandated_reporter_intakes_screened_in/n_nonmandated_reporter_intakes) %>%
  mutate_if(is.numeric, ~round(.x, digits = 2))
  
d_neighborhood %>%
  st_drop_geometry() %>% 
  select(Neighborhood = neighborhood, 
        `Number of Intakes` = n_intakes, 
       # `Intakes Screened In` = n_intakes_screened_in,
      #  `Number of Households` = num_hh, 
       # `Number Intakes per 1000 Households` = n_intakes_per_1000hh,
        `Fraction of Intakes Screened In` = intake_fractional_screen_in,
        `Number of Intakes by Mandated Reporter` = n_mandated_reporter_intakes,
      #  `Mandated Reporter Intakes per 1000 Households` = n_intakes_by_mandated_reporter_per_1000hh,
        `Intakes by Mandated Reporter Screened In` = n_mandated_reporter_intakes_screened_in,
        `Fraction of Mandated Reporter Intakes Screened In` = intake_by_mandated_reporter_fractional_screen_in,
        `Number of Intakes by Non-Mandated Reporter` = n_nonmandated_reporter_intakes,
       # `Non-Mandated Reporter Intakes per 1000 Households` = n_intakes_by_nonmandated_reporter_per_1000hh,
        `Intakes by Non-Mandated Reporter Screened In` = n_nonmandated_reporter_intakes_screened_in,
        `Fraction of Non-Mandated Reporter Intakes Screened In` = intake_by_nonmandated_reporter_fractional_screen_in) %>%
      #  `Deprivation Index` = dep_index) %>% 
  DT::datatable()
```

